Active Damping of Rotating Positioning Platforms

### 2020-06-23 paper/paper.tex
Update paper bibliography

% Created 2020-06-22 lun. 13:27
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\begin{document}

@@

\section{Introduction}
\label{sec:orgd20252d}
\label{sec:introduction}
\cite{dehaeze18_sampl_stabil_for_tomog_exper}

\section{System Under Study}
\label{sec:orgacbe1ae}
\subsection{Rotating Positioning Platform}
\label{sec:org07e4fc8}
Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/rotating_xy_platform.pdf}
\caption{\label{fig:rotating_xy_platform}Figure caption}
\end{figure}

@@

\subsection{Equation of Motion}
\label{sec:orgac1a52a}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).

@@

Dissipation function \(R\)
Kinetic energy \(T\)
Potential energy \(V\)
\begin{subequations}
\label{eq:energy_inertial_frame}
  \begin{align}
    T & = \frac{1}{2} m \left( \left( \dot{u} - \Omega v \right)^2 + \left( \dot{v} + \Omega u \right)^2 \right) \\
    R & = \frac{1}{2} c \left( \dot{u}^2 + \dot{v}^2 \right) \\
    V & = \frac{1}{2} k \left( u^2 + v^2 \right)
  \end{align}
\end{subequations}

The Lagrangian is the kinetic energy minus the potential energy:
\begin{equation}
\label{eq:lagrangian_inertial_frame}
L = T - V
\end{equation}

From the Lagrange's equations of the second kind \eqref{eq:lagrange_second_kind}, the equation of motion \eqref{eq:eom_mixed} is obtained (\(q_1 = u\), \(q_2 = v\)).
\begin{equation}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation}

\begin{equation}
  \frac{d}{dt} \left( \frac{\partial T}{\partial \dot{q}_i} \right) - \frac{\partial T}{\partial q_i} + \frac{\partial R}{\partial \dot{q}_i} - \frac{\partial V}{\partial q_i} = Q_i
\end{equation}

with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(F_u\) and \(F_v\)).

@@

@@

\begin{equation}
\label{eq:lagrange_second_kind}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_j} \right) = \frac{\partial L}{\partial q_j}
\end{equation}

\begin{subequations}
\label{eq:eom_mixed}
  \begin{align}
    m\ddot{x} + kx = F_u \cos{\theta} - F_v \sin{\theta}\\
    m\ddot{y} + ky = F_u \sin{\theta} + F_v \cos{\theta}
  \end{align}
\end{subequations}

Performing the change coordinates from \((x, y)\) to \((d_x, d_y, \theta)\):
\begin{subequations}
  \begin{align}
    x & = d_u \cos{\theta} - d_v \sin{\theta}\\
    y & = d_u \sin{\theta} + d_v \cos{\theta}
  \end{align}
\end{subequations}

Gives
\begin{subequations}
\label{eq:oem_coupled}
  \begin{align}
    m \ddot{d_u} + (k - m\dot{\theta}^2) d_u &= F_u + 2 m\dot{d_v}\dot{\theta} + m d_v\ddot{\theta} \label{eq:du_coupled} \\
    m \ddot{d_v} + (k \underbrace{-\ m\dot{\theta}^2}_{\text{Centrif.}}) d_v &= F_v \underbrace{-\ 2 m\dot{d_u}\dot{\theta}}_{\text{Coriolis}} \underbrace{-\ m d_u\ddot{\theta}}_{\text{Euler}} \label{eq:dv_coupled}
  \end{align}
\end{subequations}

We obtain two differential equations that are coupled through:
\begin{itemize}
\item \textbf{Euler forces}: \(m d_v \ddot{\theta}\)
\item \textbf{Coriolis forces}: \(2 m \dot{d_v} \dot{\theta}\)
\end{itemize}

\subsection{Constant Rotating Speed}
\label{sec:org47aaeee}
To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

@@

\section{Integral Force Feedback}
\label{sec:org78c2eab}
\subsection{Control Schematic}
\label{sec:org6a00238}

\subsection{Equations}
\label{sec:org5480f1b}

\subsection{Plant Dynamics}
\label{sec:orgbb0952e}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
\caption{\label{fig:root_locus_pure_iff}Figure caption}
\end{figure}

\subsection{Physical Interpretation}
\label{sec:orgdb25e2c}

\section{Integral Force Feedback with Low Pass Filters}
\label{sec:org2985d35}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
\end{figure}

\section{Integral Force Feedback with Parallel Springs}
\label{sec:orga4142a5}

@@

\section{Direct Velocity Feedback}
\label{sec:org6a1be4f}

@@

\section{Comparison of the Proposed Active Damping Techniques}
\label{sec:orga9658c0}

@@

\section{Conclusion}
\label{sec:orgcdf948f}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:org6c21e13}

>>>>

% Created 2020-06-22 lun. 17:38
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\begin{document}

@@

\section{Introduction}
\label{sec:org67e0a4e}
\label{sec:introduction}
\cite{dehaeze18_sampl_stabil_for_tomog_exper}

\section{System Under Study}
\label{sec:org85bcde2}
\subsection{Rotating Positioning Platform}
\label{sec:org4959a5e}
Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system.pdf}
\caption{\label{fig:rotating_xy_platform}Figure caption}
\end{figure}

@@

\subsection{Equation of Motion}
\label{sec:orgdb109d9}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).

@@

Dissipation function \(R\)
Kinetic energy \(T\)
Potential energy \(V\)
\begin{subequations}
  \begin{align}
    T & = \frac{1}{2} m \left( \left( \dot{u} - \Omega v \right)^2 + \left( \dot{v} + \Omega u \right)^2 \right) \\
    R & = \frac{1}{2} c \left( \dot{u}^2 + \dot{v}^2 \right) \\
    V & = \frac{1}{2} k \left( u^2 + v^2 \right)
  \end{align}
\end{subequations}

The Lagrangian is the kinetic energy minus the potential energy:
\begin{equation}
L = T - V
\end{equation}

From the Lagrange's equations of the second kind \eqref{eq:lagrange_second_kind}, the equation of motion \eqref{eq:eom_mixed} is obtained (\(q_1 = u\), \(q_2 = v\)).
\begin{equation}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation}
with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).

@@

\begin{itemize}
\item Coriolis Forces: coupling
\item Centrifugal forces: negative stiffness
\end{itemize}

\subsection{Transfer Functions in the Laplace domain}
\label{sec:orgfcd3def}

@@

\subsection{Constant Rotating Speed}
\label{sec:org81c7074}
To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

@@

\section{Integral Force Feedback}
\label{sec:orgc6c1b99}
\subsection{Control Schematic}
\label{sec:orgb93b297}

Force Sensors are added in series with the actuators as shown in Figure \ref{fig:system_iff}.

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_iff.pdf}
\caption{\label{fig:system_iff}System with Force Sensors in Series with the Actuators. Decentralized Integral Force Feedback is used}
\end{figure}

\subsection{Equations}
\label{sec:org4072ea4}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

Which then gives:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\bm{G}_{f}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\frac{1}{G_{fp}}
\begin{bmatrix}
  G_{fz} & -G_{fc} \\
  G_{fc} &  G_{fz}
\end{bmatrix}
\begin{bmatrix} F_u \\ F_v \end{bmatrix}
\end{equation}

\begin{align}
  G_{fp} &= \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right)^2 + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{fz} &= \left( \frac{s^2}{{\omega_0}^2} - \frac{\Omega^2}{{\omega_0}^2} \right) \left( \frac{s^2}{{\omega_0}^2} + 2 \xi \frac{s}{\omega_0} + 1 - \frac{{\Omega}^2}{{\omega_0}^2} \right) + \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)^2 \\
  G_{fc} &= \left( 2 \xi \frac{s}{\omega_0} + 1 \right) \left( 2 \frac{\Omega}{\omega_0} \frac{s}{\omega_0} \right)
\end{align}

\subsection{Plant Dynamics}
\label{sec:org0250ac0}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
\caption{\label{fig:root_locus_pure_iff}Root Locus}
\end{figure}

\subsection{Physical Interpretation}
\label{sec:orgb2d79d2}

At low frequency, the gain is very large and thus no force is transmitted between the payload and the rotating stage.
This means that at low frequency, the system is decoupled (the force sensor removed) and thus the system is unstable.

\section{Integral Force Feedback with High Pass Filters}
\label{sec:orgabf7a6a}
\subsection{Modification of the Control Low}
\label{sec:org4766bd6}

\subsection{Close Loop Analysis}
\label{sec:org4c639fd}

@@

\subsection{Optimal Cut-Off Frequency}
\label{sec:orge829a45}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff_bis.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
\caption{\label{fig:mod_iff_damping_wi}Figure caption}
\end{figure}

\section{Integral Force Feedback with Parallel Springs}
\label{sec:orgd96ea25}

@@

\section{Direct Velocity Feedback}
\label{sec:org027d051}

@@

\section{Comparison of the Proposed Active Damping Techniques}
\label{sec:org1eaa959}

@@

\section{Conclusion}
\label{sec:org1b2b4ae}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:org2ae16a5}
